\documentclass{article}



%\usepackage{amssymb,latexsym,amsmath}
\usepackage{amssymb,latexsym}
%\usepackage{makeidx} 
%\makeindex

%\usepackage[dvips,matrix,arrow,ps,color,line,curve,frame]{xy}

%\usepackage{graphicx}

\usepackage[pdftex]{graphicx}

%\usepackage{parsetree}
\usepackage{hyperref}



\hoffset-0.64cm
\voffset-2.14cm


\textheight23.8cm

\setlength{\textwidth}{14.cm}



\begin{document}


\pagestyle{plain}










\newtheorem{theorem}{Theorem}[section]

\newtheorem{proposition}[theorem]{Proposition}

\newtheorem{lema}[theorem]{Lemma}

\newtheorem{corollary}[theorem]{Corollary}

\newtheorem{definition}[theorem]{Definition}

\newtheorem{remark}[theorem]{Remark}

\newtheorem{exempl}{Example}[section]

\newenvironment{example}{\begin{exempl}  \em}{\hfill $\square$

\end{exempl}}  \vspace{.5cm}









\renewcommand{\contentsname}{ }




\title{The EM rewrite system}

\author{Marius Buliga \\ 
\\
Institute of Mathematics, Romanian Academy \\
P.O. BOX 1-764, RO 014700\\
Bucure\c sti, Romania\\
{\footnotesize Marius.Buliga@imar.ro}}  \vspace{.5cm}







\date{This version: \today}






\maketitle


\begin{abstract}
We study emergent algebras as a term rewrite system. 

\end{abstract}


%\tableofcontents


%\newpage

\include{tex/finite_terms}

\include{tex/patt_match}
 
\include{tex/r1_r2}

\include{tex/irq}

\include{tex/comm}

\include{tex/binary}

\include{tex/approx_op}

\include{tex/limterms}

\include{tex/em_meta}

\include{tex/conical}

%\include{tex/tangles}


\begin{thebibliography}{99}


\bibitem{buligaglc} M. Buliga, Graphic lambda calculus. {\it Complex Systems} {\bf 22}, 4 (2013), 311-360. \\ 
\href{https://arxiv.org/abs/1305.5786}{arXiv:1305.5786}

\bibitem{buligairq} M. Buliga, Emergent algebras, \href{https://arxiv.org/abs/0907.1520}{arXiv:0907.1520}

\bibitem{buligadil1} M. Buliga, Dilatation structures I. Fundamentals, {\it 
J. Gen. Lie Theory Appl.},  {\bf 1} (2007),  2, 65-95. \\ 
\href{https://arxiv.org/abs/math/0608536}{arXiv:math/0608536}


\bibitem{buligainf} M, Buliga, Infinitesimal affine geometry of metric spaces endowed with a dilatation structure, {\it Houston Journal of Mathematics}, {\bf 36}, 1 (2010), 91-136. \\ 
\href{https://arxiv.org/abs/0804.0135}{arXiv:math/0608536}


\bibitem{buligabraided} M. Buliga, Braided spaces with dilations and sub-riemannian symmetric spaces, in: Geometry. Exploratory Workshop on Differential Geometry and its Applications, eds. D. Andrica, S. Moroianu, Cluj-Napoca 2011, 21-35. \\   
\href{https://arxiv.org/abs/1005.5031}{arXiv:0804.0135}


\bibitem{buligachora} M. Buliga, Computing with space: a tangle formalism for chora and difference, \href{https://arxiv.org/abs/1103.6007}{arXiv:1103.6007}




%\bibitem{polyak} M. Polyak,  Minimal generating sets of Reidemeister moves,  \href{http://arxiv.org/abs/0908.3127}{arXiv:0908.3127}

%\bibitem{lodayr} J.-L. Loday, M.O. Ronco, Hopf Algebra of the  planar  Binary Trees, {\it Advances in Math.}, {\bf 139} (1998), 293-309

\bibitem{graphiclambdaknots} M. Buliga, Graphic lambda calculus and knot diagrams, \href{http://arxiv.org/abs/1211.1604}{arXiv:1211.1604}


\bibitem{graphiclambdamoves} M. Buliga, Local and global moves on locally planar trivalent graphs, lambda calculus and lambda-Scale, \href{http://arxiv.org/abs/1207.0332}{arXiv:1207.0332} 

\bibitem{lambdascale} M. Buliga, Lambda-Scale, a lambda calculus for spaces with dilations,  \href{http://arxiv.org/abs/1205.0139}{arXiv:1205.0139}


\bibitem{siebert} E. Siebert, Contractive automorphisms on locally compact groups, Math. Z., 191, 73-90, (1986)


\end{thebibliography}


\end{document}

